### 2018-11-30 README.Rmd
add repro note and rebuild docs

@@

``` r
devtools::install_github("kevinykuo/deeptriangle)
```

@@

```{r, message = FALSE, cache = TRUE}
library(deeptriangle)
library(tidyverse)
library(keras)

@@

predictions <- lobs %>%
  map(
    function(x) {
      # clear session and instantiate model
      k_clear_session()
      model <- dt_model()

@@

      # clear session and reinstantiate model
      k_clear_session()
      model <- dt_model()

@@

```{r}
model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  gather(metric, value, mape, rmspe)
```

>>>>

**Note: Due to changes in some library dependencies over time, the results may not reproduce exactly depending on when you installed TensorFlow, but the conclusions of the paper remain unchanged. The results below are generated using TensorFlow 1.10 and Keras 2.2.**

@@

``` r
devtools::install_github("kevinykuo/deeptriangle")
```

@@

```{r, message = FALSE, warning = FALSE, cache = FALSE}
library(deeptriangle)
library(tidyverse)
library(keras)

use_implementation("tensorflow")

@@

predictions <- lobs %>%
  map(
    function(x) {
      # reinstantiate model
      model <- dt_model()

      model %>%
        keras::compile(
          optimizer = keras::optimizer_adam(amsgrad = TRUE),
          loss = "mae",
          loss_weights = c(0.8, 0.2)
      )

@@

      model <- dt_model()

      model %>% keras::compile(
        optimizer = keras::optimizer_adam(amsgrad = TRUE),
        loss = "mae",
        loss_weights = c(0.8, 0.2)
      )

@@

```{r, message = FALSE}
model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(read_csv("analysis/automl_results.csv")) %>%
  gather(metric, value, mape, rmspe)
```
